On Secure Delegation of SampBQP with a Classical Client

### 2020-02-02 blind.tex
Wrap up blindness first draft

The construction is obvious, \Ethan{Maybe still write it out...? Or maybe not?} so we directly go into analysis.

@@

	\Ethan{Check how much of the following still applies before erasing}
	Suppose $\bbV$ accepts $\bbP'$ at least $\delta$ of the time.

	Then the $\QPIP_0$ delegation must accept at least that often too,
	so the client will receive a sample from $\mathsf{Eval}_{evk}(C, \tilde{x})$ with at most inverse poly error. \Ethan{security param?}

	The verifier ends up with a state within inverse poly distance to
		$$\widehat{\mathsf{QHE.Dec}_{sk}}\circ\Lambda'(\tilde{C}(\tilde{x}))$$
		$$=\Lambda\circ\mathsf{QHE.Dec}_{sk}(\tilde{C}(\tilde{x}))$$
		$$=\Lambda\circ\mathsf{QHE.Dec}_{sk}(\mathsf{QHE.Eval}_{evk}(C, \tilde{x}))$$

	By the properties of homomoprhic encryption, with overwhelming probability this is indistinguishable to \Ethan{Check if it's true} $\Lambda(C(x))$
\end{proof}

>>>>

The construction is obvious, \Ethan{Maybe still write it out...? Or maybe not?} so we directly go into analysis. \Ethan{Need to remember security param if we write this out}

@@

	As for soundness, a cheating prover cannot do better under this compiliation, since each message still decodes to some plaintext.

	In other words, anything a cheating prover can do after the compiliation, there exists a corresponding strategy in the version before.
	\Ethan {Ahhhh this is not rigorous at all}
\end{proof}

### 2020-02-02 bqp.tex
Updates from Overleaf
Make flow of blind then fully classical consistent
Wrap up blindness first draft

\section{Constant-Round Blind Delegation for BQP}

\Ethan{Need to define QPIP for both decision and sampling problems and point out the differences then}

We'll define the following protocol for $\BQP$ which we later generalize.

@@

There exists some certificate for both $x\in L$ and $x\notin L\Rightarrow x\in\overline{L}$, since $L, \overline{L}\in\QMA$.
In fact, they have the same certificate, and the certificate can be check using only $X$ and $Z$ measurements, which we'll call $\ket{\psi_x}$. \Ethan{TODO cite textbook for this}

@@

\begin{algorithm}
	\caption{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	\begin{algorithmic}[1]
		\State Let $\lambda$ be the security parameter.
		\State Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda)$ to get $pk, sk$.
		\State The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
		\State The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ and $pk$ to the prover
		\State The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
		\State The verifier measures the incoming ciphertext according to \autoref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates
		\State The verifier decodes the measurement results
		\State The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{algorithmic}
\end{algorithm}

@@

Now we can simply apply the following results from \Ethan{TODO cite}...

\begin{thm}
	There is a way to compile a $\QPIP_1$ protocol with the following properties:
	\begin{itemize}
		\item classical inputs
		\item only X/Z measurements
		\item negl. completeness and soundness
	\end{itemize}
	into a $\QPIP_0$ protocol with negl. completeness and soundness
\end{thm}

With this result, we now achieve...
\begin{thm}
	There exists...
\end{thm}
\begin{proof}
	Just compile A through B...
\end{proof}

>>>>

\section{Constant-Round Blind Delegation for BQP}
\label{sec:BlindBQP}

In this section we present our constant-round blind delegation protocol for $\BQP$.
We'll later construct a protocol for $\SampBQP$ following the same flow of logic, albeit requiring more careful analysis.

\begin{thm}
	\Ethan{Main theorem of the section}
	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}

We'll construct this protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.

@@

There exists some certificate for both $x\in L$ and $x\notin L\Rightarrow x\in\overline{L}$, since $L, \overline{L}\in\QMA$.
In fact, they have the same certificate, which we'll call $\ket{\psi_x}$. See the excellent text \cite{kitaev2002classical} for details.
According to \cite{PhysRevA.93.022326}, the certificate can be check using only $X$ and $Z$ measurements.
We'll also summarize said proofs in \cref{sec:Hamiltonian} for our $\SampBQP$ construction.

@@

\begin{algorithm}
	\caption{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	\begin{algorithmic}[1]
		\State Let $\lambda$ be the security parameter.
		\State Let $L$ be the depth of the circuit corresponding to $\cF$
		\State Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda, L)$ to get $pk, sk$.
		\State The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
		\State The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ and $pk$ to the prover
		\State The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
		\State The verifier measures the incoming ciphertext according to \autoref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates
		\State The verifier decodes the measurement results
		\State The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{algorithmic}
\end{algorithm}

@@

Now we can simply apply the following results from \cite{parallelrep} to obtain a blind and constant-round for $\QPIP_0$ with negligible completeness and soundness.
\begin{thm}
	There is a compiler that takes a $\QPIP_1$ protocol with the following properties:
	\begin{itemize}
		\item classical inputs
		\item client uses only X/Z measurements
		\item negl. completeness and soundness
	\end{itemize}
	and outputs a corresponding $\QPIP_0$ protocol with negl. completeness and soundness \Ethan{same inputs...?}
\end{thm}

### 2020-02-02 preliminaries.tex
Wrap up blindness first draft

\begin{dfn}
	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{Keygen}(1^\lambda, 1^D)\rightarrow(pk, evk, sk)$
		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

$\mathsf{HE}$ also satisfies, with all but negligible probability in $\lambda$, that
$$\mathsf{HE.Dec}_{sk}(\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
where $f$ is specified by a circuit of depth at most $D$.

>>>>

\begin{dfn}
	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{Keygen}(1^\lambda, 1^L)\rightarrow(pk, evk, sk)$
		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

\Ethan{TODO Check if Dec has to work all the time or just overwhelming probability (and if so, over what)}

$\mathsf{HE}$ also satisfies, with overwhelming probability in $\lambda$, that
$$\mathsf{HE.Dec}_{sk}(\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
where $f$ is specified by a circuit of depth at most $L$.
